---
title: "Map"
date: "2024-01-03"
output: html_document
---

## Map of shelters and points of invinsibility
 
Map of bomb shelters and points of invincibility used during air attacks.

Disclaimer: Map is not illustrate a real location of shelters due to the security reasons. 
```{r, echo = F, warning=FALSE}
suppressPackageStartupMessages(
library(dplyr)
  )
library(leaflet)

df <- data.frame(lat = runif(20, 50.40, 50.50), lng = runif(20, 30.35, 30.45), col = sample(c('red', 'blue','green'), 20, replace = T), stringAsFactor = F)

suppressMessages(
  df %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(color = df$col) %>% 
  addLegend(labels = c('bomb shelters', 'points of invincibility (charging and heating station)', 'others'), colors = c("blue", "red","green"))
    )
```
Disclaimer: Map is not illustrate real location of shelters due to security reasons. 

# Population density

Disclaimer: data on the population density is randomly simulated and is not reliable
```{r, echo = F}
district <- data.frame(
                        pop = runif(30, min = min(61493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346), 
                                max = c(61493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346)),
                        lat = runif(30, 50.40, 50.50),
                        lng = runif(30, 30.35, 30.45))

suppressMessages(
  district %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(weight = 1, radius = sqrt(district$pop)/20) %>% 
  addRectangles(lng1 = 30.35,lat1 = 50.4, lng2 = 30.45, lat2 = 50.5))
```
Disclaimer: data on the population density is randomly simulated and is not reliable.
